Quality control for the target decoy approach for peptide identification

### 2022-11-13 index.Rmd
update index.Rmd

This repo contains all necessary files to perform all data analyses and generate all figures for our paper: "Quality control for the target decoy approach for peptide identification"

Generate all figures: [paper_figures](./paper_figures.html)
Document with supplementary figures: [supplementary_figures](./paper_supplementary.pdf)

>>>>

This repository contains all necessary files to perform all data analyses and generate all figures for our paper: "Quality control for the target decoy approach for peptide identification"

- Generate all Figures: [paper_figures](./paper_figures.html)

- Document with Supplementary Figures: [supplementary_figures](./paper_supplementary.pdf)
